---
title: "Jambase API"
author: "Mike Kaminski"
date: "2023-09-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r}
library(httr)
library(lubridate)
library(dplyr)
# url for the events page
url <- "https://www.jambase.com/jb-api/v1/events"

# date to get the next few months
future_date <- Sys.Date() %m+% months(3)

# gets the number of shows for the future date
countString <- list(apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
                    geoCityId ="jambase:4230765",
                    eventDateTo = future_date) # this is the Chicago geoCityId

countResponse <- VERB("GET",
                      url,
                      query = countString,
                      content_type("application/octet-stream"),
                      accept("application/json"))

countContent <- content(countResponse,"parsed")

numShows <- countContent$pagination$totalItems

# numPages <- countContent$pagination$totalPages

# queryString <- list(apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
#                     geoCityId ="jambase:4230765",
#                     perPage = 100,
#                     eventDateTo = future_date)
# 
# response <- VERB("GET", url, query = queryString, content_type("application/octet-stream"), accept("application/json"))
# all <- content(response, "parsed")
```

# Gets all the upcoming shows.
```{r}
# create an empty list to store the results
all_results <- list()

# Define  common parameters
common_params <- list(
  apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
  geoCityId = "jambase:4230765",
  perPage = 100,
  eventDateTo = future_date,
  expandExternalIdentifiers = "true"
)

# Specify the number of pages to fetch
num_pages <- ceiling(numShows/100)

# Loop through each page
for (page in 1:num_pages) {
  # Create a copy of the common parameters and set the 'page' parameter
  query_params <- c(common_params, page = page)
  
  # Send the HTTP request
  response <- VERB("GET", url, query = query_params, content_type("application/octet-stream"), accept("application/json"))
  
  # Parse and store the response in the list
  all_results[[page]] <- content(response, "parsed")
}


all_results[[1]]$events[[1]]$performer[[1]]$`x-externalIdentifiers`[[5]]$identifier[[1]]

str(all_results[[1]]$events[[1]]$performer[[1]])
```

# Gets all the venues
If there's more than 1 performer at the event, then the venue is repeated.
```{r}
# Original Code
# venues <- lapply(all_results, function(x) {
#   lapply(x$events, function(event) {
#     event$location$name
#   })
# })

venues <-
  lapply(all_results, function(x) {
    lapply(x$events, function(event) {
      if (length(event$performer) > 1) {
        names <- rep(event$location$name, length(event$performer))
      } else if (length(event$performer) == 1) {
        names <- event$location$name
      } else {
        names <- NA  # or any other value you want to use for missing names
      }
      names
    })
  })

venues_col <- unlist(venues) %>% as.data.frame()
colnames(venues_col) <- "venue"
```

# Gets the date of the show
If there's more than 1 performer at the event, then the date is repeated.
```{r}
# Original Code
# shows <- lapply(all_results, function(x) {
#   lapply(x$events, function(event) {
#     event$startDate
#   })
# })

shows <-
  lapply(all_results, function(x) {
    lapply(x$events, function(event) {
      if (length(event$performer) > 1) {
        names <- rep(event$startDate, length(event$performer))
      } else if (length(event$performer) == 1) {
        names <- event$startDate
      } else {
        names <- NA  # or any other value you want to use for missing names
      }
      names
    })
  })

shows_col <- unlist(shows) %>% as.data.frame()
colnames(shows_col) <- "show_date"
```


# old code to get artist name
```{r}
# artists <-
#   value <- lapply(all_results, function(x) {
#   lapply(x$events, function(event) {
#     if (length(event$performer) > 1) {
#       names <- lapply(event$performer, function(performer) performer$name)
#     } else if (length(event$performer) == 1) {
#       names <- event$performer[[1]]$name
#     }
#     names
#   })
# })
# 
# artists_col <- unlist(artists) %>% as.data.frame()
# colnames(artists_col) <- "artists"
#   
```

# gets the performance date for each band
```{r}
perf_date <-
  venues <- lapply(all_results, function(x) {
  lapply(x$events, function(event) {
    if (length(event$performer) > 1) {
      names <- lapply(event$performer, function(performer) performer$`x-performanceDate`)
    } else if (length(event$performer) == 1) {
      names <- event$performer[[1]]$`x-performanceDate`
    }
    names
  })
})

perf_col <- unlist(perf_date) %>% as.data.frame()
colnames(perf_col) <- "perfdate"
```

# New code to get artist name as well as spotify_id
```{r}
# Initialize an empty list to store performer names and Spotify identifiers
performer_data <- list()

# Iterate through each result in all_results
for (result in all_results) {
  # Iterate through each event in the result
  for (event in result$events) {
    # Check if the event has performers
    if (length(event$performer) > 0) {
      # Iterate through each performer in the event
      for (performer in event$performer) {
        # Check if performer has external identifiers
        if (!is.null(performer$`x-externalIdentifiers`)) {
          # Find the entry with source "spotify"
          spotify_entry <- lapply(performer$`x-externalIdentifiers`, function(entry) {
            if (entry$source == "spotify") {
              return(entry$identifier[[1]])
            }
          })
          # Remove NULL values (entries other than "spotify")
          spotify_entry <- Filter(function(x) !is.null(x), spotify_entry)
          
          # Get the performer name
          performer_name <- performer$name
          
          # Create a list containing both performer name and Spotify identifiers
          performer_data_entry <- list(name = performer_name, spotify = spotify_entry)
          
          # Add the data for this performer to the list
          performer_data <- append(performer_data, list(performer_data_entry))
        }
      }
    }
  }
}

# performer_data[[1]]$name
# performer_data[[1]]$spotify
# str(performer_data[[1]])

performer_df <- data.frame(
  Name = sapply(performer_data, function(entry) entry$name),
  Spotify = sapply(performer_data, function(entry) {
    if (length(entry$spotify) > 0) {
      return(entry$spotify[[1]])
    } else {
      return(NA)
    }
  })
)

```


# Merges dataframes
```{r}
upcoming_shows <- cbind(venues_col,shows_col,performer_df) %>%
  mutate(show_date = as.Date(show_date,format = "%Y-%m-%d")) %>%
  filter(!grepl("Sofar",venue, ignore.case = TRUE)) %>%
  filter(!(venue %in% c("Douglas Park",
                     "Hyde Park Jazz",
                     "Fairmont Chicago Millennium Park",
                     "Epiphany Center for the Arts",
                     "On Tour Brewing")))

upcoming_shows %>% group_by(venue) %>% summarise(count = n()) %>% arrange(desc(count))
upcoming_shows %>% summarise(count = n()) %>% arrange(desc(count))
upcoming_shows %>% filter(venue %in% 'United Center')
```

# Removes duplicate Spotify Ids
```{r}
upcoming_shows1 <- upcoming_shows %>% distinct(Name, Spotify)
```


# END

# old Gets Spotify Ids using artists
```{r}

# Goes to the artists URL
url <- "https://www.jambase.com/jb-api/v1/artists"

# defines variable to loop through
# all_artists <- upcoming_shows %>% distinct(artists)
all_artists <- upcoming_shows$artists

# Initialize an empty list to store each artist
artistStringsList <- list()

# Loop through each artist in the "artists" column
for (artist in all_artists) {  
  # Create a countString for the current artist
  artistString <- list(
    apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
    artistName = artist,
    expandExternalIdentifiers = TRUE
  )
  
  artistResponse <- VERB("GET",
                      url,
                      query = artistString,
                      content_type("application/octet-stream"),
                      accept("application/json"))
  
  artistContent <- content(artistResponse,"parsed")
  
  # Append the artistString to the list
  artistStringsList <- append(artistStringsList, list(artistContent))
}



```

# old Spotify URLs
```{r}
# Initialize an empty list to store the Spotify URLs
spotify_urls <- list()

# Iterate through each countString in countStringsList
for (artistString in artistStringsList) {
  # Extract the "artists" list
  artists_list <- artistString$artists
  
  # Initialize a variable to store the Spotify URL for the current artist
  spotify_url <- NULL
  
  # Iterate through each artist in the "artists" list
  for (artist in artists_list) {
    # Extract the "sameAs" list for the current artist
    sameAs_list <- artist$sameAs
    
    # Find the item with identifier "spotify" in the "sameAs" list
    spotify_item <- NULL
    for (item in sameAs_list) {
      if (item$identifier == "spotify") {
        spotify_item <- item
        break  # Exit the loop once found
      }
    }
    
    # If a Spotify URL is found, extract it
    if (!is.null(spotify_item)) {
      spotify_url <- spotify_item$url
      break  # Exit the loop once a Spotify URL is extracted
    }
  }
  
  # Add the Spotify URL to the list
  spotify_urls <- append(spotify_urls, list(spotify_url))
}

# Now spotify_urls contains the list of Spotify URLs for each artist in countStringsList

# Define a function to extract the identifier from a Spotify URL
extract_spotify_identifier <- function(spotify_url) {
  if (!is.null(spotify_url)) {
    return(sub(".*/artist/([^/]+)$", "\\1", spotify_url))
  } else {
    return(NULL)
  }
}

# Use lapply to apply the function to each element in spotify_urls
spotify_identifiers <- lapply(spotify_identifiers, function(x) ifelse(is.null(x), NA, x))
spotify_df <- data.frame(SpotifyID = unlist(spotify_identifiers))

str(spotify_identifiers)
```

# New  psotify URls
```{r}
# Initialize an empty list to store the Spotify URLs
spotify_urls <- list()

# Initialize an empty list to store the artist names
artist_names <- list()

# Iterate through each artistString in artistStringsList
for (artistString in artistStringsList) {
  # Extract the "artists" list
  artists_list <- artistString$artists
  
  # Initialize a variable to store the Spotify URL for the current artist
  spotify_url <- NULL
  
  # Initialize a variable to store the artist name for the current artist
  artist_name <- NULL
  
  # Iterate through each artist in the "artists" list
  for (artist in artists_list) {
    # Extract the "sameAs" list for the current artist
    sameAs_list <- artist$sameAs
    
    # Find the item with identifier "spotify" in the "sameAs" list
    spotify_item <- NULL
    for (item in sameAs_list) {
      if (item$identifier == "spotify") {
        spotify_item <- item
        break  # Exit the loop once found
      }
    }
    
    # Extract the artist name
    artist_name <- artist$name  
    
    # If a Spotify URL is found, extract it
    if (!is.null(spotify_item)) {
      spotify_url <- spotify_item$url
      break  # Exit the loop once a Spotify URL is extracted
    }
  }
  
  # Add the Spotify URL to the list
  spotify_urls <- append(spotify_urls, list(spotify_url))
  
  # Add the artist name to the list
  artist_names <- append(artist_names, list(artist_name))
}

# Define a function to extract the identifier from a Spotify URL
extract_spotify_identifier <- function(spotify_url) {
  if (!is.null(spotify_url)) {
    return(sub(".*/artist/([^/]+)$", "\\1", spotify_url))
  } else {
    return(NULL)
  }
}

# Use lapply to apply the function to each element in spotify_urls
spotify_identifiers <- lapply(spotify_urls, function(url) {
  if (!is.null(url)) {
    extract_spotify_identifier(url)
  } else {
    NA
  }
})


spotify_df <- data.frame(SpotifyID = unlist(spotify_identifiers))
artists_df <- data.frame(artist = unlist(artist_names))
final_df <- cbind(artists_df,spotify_df) %>% 
  distinct(artist, SpotifyID)

```



# External IDS?
```{r}
# url for the events page
url <- "https://www.jambase.com/jb-api/v1/artists"

# date to get the next few months
future_date <- Sys.Date() %m+% months(1)

# gets the number of shows for the future date
countString <- list(apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
                    geoCityId ="jambase:4230765",
                    artistName = '%Bayside%',
                    expandExternalIdentifiers = TRUE) # this is the Chicago geoCityId
                    # eventDateTo = future_date) 

countResponse <- VERB("GET",
                      url,
                      query = countString,
                      content_type("application/octet-stream"),
                      accept("application/json"))

countContent <- content(countResponse,"parsed")


```

```{r}
url <- "https://www.jambase.com/jb-api/v1/artists"
tes <- head(upcoming_shows$artists,5)
artist_names <- paste(tes, collapse = "|")
artist_names <- paste(artist_names, collapse = "")

# gets the number of shows for the future date
countString <- list(apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
                    artistName = tes,
                    expandExternalIdentifiers = TRUE) # this is the Chicago geoCityId
                    # eventDateTo = future_date) 

countResponse <- VERB("GET",
                      url,
                      query = countStringsList,
                      content_type("application/octet-stream"),
                      accept("application/json"))

countContent <- content(countResponse,"parsed")

```
```{r}
# Initialize an empty list to store the countStrings for each artist
countStringsList <- list()

# Loop through each artist in the "artists" column
# for (artist in upcoming_shows$artists) {
for (artist in tes) {  
  # Create a countString for the current artist
  countString <- list(
    apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
    artistName = artist,
    expandExternalIdentifiers = TRUE
  )
  
  countResponse <- VERB("GET",
                      url,
                      query = countString,
                      content_type("application/octet-stream"),
                      accept("application/json"))
  
  countContent <- content(countResponse,"parsed")
  
  # Append the countString to the list
  countStringsList <- append(countStringsList, list(countContent))
}

####################

# Initialize an empty list to store the Spotify URLs
spotify_urls <- list()

# Iterate through each countString in countStringsList
for (countString in countStringsList) {
  # Extract the "artists" list
  artists_list <- countString$artists
  
  # Initialize a variable to store the Spotify URL for the current artist
  spotify_url <- NULL
  
  # Iterate through each artist in the "artists" list
  for (artist in artists_list) {
    # Extract the "sameAs" list for the current artist
    sameAs_list <- artist$sameAs
    
    # Find the item with identifier "spotify" in the "sameAs" list
    spotify_item <- NULL
    for (item in sameAs_list) {
      if (item$identifier == "spotify") {
        spotify_item <- item
        break  # Exit the loop once found
      }
    }
    
    # If a Spotify URL is found, extract it
    if (!is.null(spotify_item)) {
      spotify_url <- spotify_item$url
      break  # Exit the loop once a Spotify URL is extracted
    }
  }
  
  # Add the Spotify URL to the list
  spotify_urls <- append(spotify_urls, list(spotify_url))
}

# Now spotify_urls contains the list of Spotify URLs for each artist in countStringsList

# Define a function to extract the identifier from a Spotify URL
extract_spotify_identifier <- function(spotify_url) {
  if (!is.null(spotify_url)) {
    return(sub(".*/artist/([^/]+)$", "\\1", spotify_url))
  } else {
    return(NULL)
  }
}

# Use lapply to apply the function to each element in spotify_urls
spotify_identifiers <- lapply(spotify_urls, extract_spotify_identifier)

# Now spotify_identifiers contains the extracted identifiers with the same structure



str(spotify_urls)
# Now countStringsList contains a list of countStrings for each artist
countStringsList[[1]]$artists[[1]]$sameAs[[2]]$url
str(countStringsList[[1]])
```



# Spotify
```{r}
countStringsList$artists[[1]]$sameAs[[4]]$identifier

str(countContent$artists[[1]]$sameAs)

spotify <-
  lapply(all_results, function(x) {
    lapply(x$events, function(event) {
      if (length(event$performer) > 1) {
        names <- rep(event$location$name, length(event$performer))
      } else if (length(event$performer) == 1) {
        names <- event$location$name
      } else {
        names <- NA  # or any other value you want to use for missing names
      }
      names
    })
  })

venues_col <- unlist(venues) %>% as.data.frame()
colnames(venues_col) <- "venue"
```

```{r}
# Assuming countContent$artists[[1]]$sameAs is your list
sameAs_list <- countContent$artists[[1]]$sameAs

# Initialize a variable to store the Spotify URL
spotify_url <- NULL

# Iterate through the list and find the item with identifier "Spotify"
for (item in sameAs_list) {
  if (item$identifier == "spotify") {
    spotify_url <- item$url
    break  # Exit the loop once found
  }
}

# Check if Spotify URL is found
if (!is.null(spotify_url)) {
  cat("Spotify URL:", spotify_url, "\n")
} else {
  cat("Spotify URL not found\n")
}


```



# Older/test code
```{r}
# length(all_results[[1]]$events[[27]]$performer)
# all_results[[1]]$events[[27]]$performer[[2]]$`x-performanceDate`

artists_test <-
  venues <- lapply(all_results, function(x) {
  lapply(x$events, function(event) {
    if (length(event$performer) > 1) {
      names <- lapply(event$performer, function(performer) performer$`x-performanceDate`)
    } else if (length(event$performer) == 1) {
      names <- event$performer[[1]]$`x-performanceDate`
    }
    names
  })
})

a <- unlist(artists_test) %>% as.data.frame()
colnames(artists_col) <- "perfdate"
  
```

```{r}


shows <-   
  value <- lapply(all_results, function(x) {
  lapply(x$events, function(event) {
    if (length(event$performer) > 1) {
      names <- lapply(event$startDate, function(startDate) event$startDate)
    } else if (length(event$performer) == 1) {
     names <- event$startDate
    }
    names
  })
})
shows_col <- unlist(shows) %>% as.data.frame()
colnames(shows_col) <- "show_date"
```

```{r}
# Extract $location$name for all elements
a <- lapply(all_results, function(x) {
  lapply(x$events, function(event) {
    event$location$name
  })
})
venues_col <- unlist(venues) %>% as.data.frame()
colnames(venues_col) <- "venue"
```

```{r}
a <- 
  lapply(all_results, function(x) {
    lapply(x$events, function(event) {
      if (length(event$performer) > 1) {
        names <- rep(event$location$name, length(event$performer))
      } else if (length(event$performer) == 1) {
        names <- event$location$name
      } else {
        names <- NA  # or any other value you want to use for missing names
      }
      names
    })
  })

a_col <- unlist(a) %>% as.data.frame()
colnames(a_col) <- "venue"
```

