---
title: "Jambase API"
author: "Mike Kaminski"
date: "2023-09-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


```{r libraries, include=FALSE}
library(httr)
library(lubridate)
library(spotifyr)
library(tidyverse)
library(tinyspotifyr)
```

# Jambase
## Accesses the API
```{r}

# url for the events page
url <- "https://www.jambase.com/jb-api/v1/events"

# date to get the next few months
future_date <- Sys.Date() %m+% months(1)

# gets the number of shows for the future date
countString <- list(apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
                    geoCityId ="jambase:4230765",
                    eventDateTo = future_date) # this is the Chicago geoCityId

countResponse <- VERB("GET",
                      url,
                      query = countString,
                      content_type("application/octet-stream"),
                      accept("application/json"))

countContent <- content(countResponse,"parsed")

numShows <- countContent$pagination$totalItems

```

## Gets all the upcoming shows.
```{r}
# creates an empty list to store the results
all_results <- list()

# Defines the common parameters
common_params <- list(
  apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
  geoCityId = "jambase:4230765",
  perPage = 100,
  eventDateTo = future_date,
  expandExternalIdentifiers = "true"
)

# Specifies the number of pages to fetch
num_pages <- ceiling(numShows/100)

# Loops through each page
for (page in 1:num_pages) {
  # Create a copy of the common parameters and set the 'page' parameter
  query_params <- c(common_params, page = page)
  
  # Send the HTTP request
  response <- VERB("GET", url, query = query_params, content_type("application/octet-stream"), accept("application/json"))
  
  # Parse and store the response in the list
  all_results[[page]] <- content(response, "parsed")
}


# all_results[[1]]$events[[1]]$performer[[1]]$`x-externalIdentifiers`[[5]]$identifier[[1]]
# 
# str(all_results[[1]]$events[[1]]$performer[[1]])
```

## Gets all the venues
If there's more than 1 performer at the event, then the venue is repeated.
```{r}
venues <-
  lapply(all_results, function(x) {
    lapply(x$events, function(event) {
      if (length(event$performer) > 1) {
        names <- rep(event$location$name, length(event$performer))
      } else if (length(event$performer) == 1) {
        names <- event$location$name
      } else {
        names <- NA  # or any other value you want to use for missing names
      }
      names
    })
  })

venues_col <- unlist(venues) %>% as.data.frame()
colnames(venues_col) <- "venue"
```

## Gets the date of the show
If there's more than 1 performer at the event, then the date is repeated.
```{r}
shows <-
  lapply(all_results, function(x) {
    lapply(x$events, function(event) {
      if (length(event$performer) > 1) {
        names <- rep(event$startDate, length(event$performer))
      } else if (length(event$performer) == 1) {
        names <- event$startDate
      } else {
        names <- NA  # or any other value you want to use for missing names
      }
      names
    })
  })

shows_col <- unlist(shows) %>% as.data.frame()
colnames(shows_col) <- "show_date"
```

## Gets the performance date for each band
```{r}
perf_date <-
  venues <- lapply(all_results, function(x) {
  lapply(x$events, function(event) {
    if (length(event$performer) > 1) {
      names <- lapply(event$performer, function(performer) performer$`x-performanceDate`)
    } else if (length(event$performer) == 1) {
      names <- event$performer[[1]]$`x-performanceDate`
    }
    names
  })
})

perf_col <- unlist(perf_date) %>% as.data.frame()
colnames(perf_col) <- "perfdate"
```

## Gets artist name and spotify_id for each artist
```{r}
# Initialize an empty list to store performer names and Spotify identifiers
performer_data <- list()

# Iterate through each result in all_results
for (result in all_results) {
  # Iterate through each event in the result
  for (event in result$events) {
    # Check if the event has performers
    if (length(event$performer) > 0) {
      # Iterate through each performer in the event
      for (performer in event$performer) {
        # Check if performer has external identifiers
        if (!is.null(performer$`x-externalIdentifiers`)) {
          # Find the entry with source "spotify"
          spotify_entry <- lapply(performer$`x-externalIdentifiers`, function(entry) {
            if (entry$source == "spotify") {
              return(entry$identifier[[1]])
            }
          })
          # Remove NULL values (entries other than "spotify")
          spotify_entry <- Filter(function(x) !is.null(x), spotify_entry)
          
          # Get the performer name
          performer_name <- performer$name
          
          # Create a list containing both performer name and Spotify identifiers
          performer_data_entry <- list(name = performer_name, spotify = spotify_entry)
          
          # Add the data for this performer to the list
          performer_data <- append(performer_data, list(performer_data_entry))
        }
      }
    }
  }
}

# performer_data[[1]]$name
# performer_data[[1]]$spotify
# str(performer_data[[1]])

performer_df <- data.frame(
  Name = sapply(performer_data, function(entry) entry$name),
  Spotify = sapply(performer_data, function(entry) {
    if (length(entry$spotify) > 0) {
      return(entry$spotify[[1]])
    } else {
      return(NA)
    }
  })
)
```


## Merges dataframes
```{r}
upcoming_shows <- cbind(venues_col,shows_col,performer_df) %>%
  mutate(show_date = as.Date(show_date,format = "%Y-%m-%d")) %>%
  filter(!grepl("Sofar",venue, ignore.case = TRUE)) %>%
  filter(venue %in% c(
    "Concord Music Hall",
    "The Vic Theatre",
    #"Subterranean",
    #"Beat Kitchen",
    "The Riviera Theatre",
    "Byline Bank Aragon Ballroom",
    "Radius",
    "Lincoln Hall",
    "Chop Shop",
    "Martyrs",
    "The Salt Shed",
    "House of Blues",
    "Bottom Lounge",
    "Schubas",
    "Metro",
    #"United Center",
    #"Joe’s On Weed Street",
    "Park West"
    #"Wintrust Arena",
    #"Credit Union 1 Arena"
    )
)

# upcoming_shows %>% group_by(venue) %>% summarise(count = n()) %>% arrange(desc(count))
# upcoming_shows %>% summarise(count = n()) %>% arrange(desc(count))
# upcoming_shows %>% filter(venue %in% 'United Center')
```

## Removes duplicates for when the artist plays multiple nights at the same venue
```{r}
upcoming_shows1 <- upcoming_shows  %>%
  arrange(show_date) %>%
  distinct(venue, Name, Spotify, .keep_all = TRUE)
```


# Spotify
## Sets up the environment
```{r}
Sys.setenv(SPOTIFY_CLIENT_ID = '9b5eb134223f4cb5a0c4834fa5742d9e')
Sys.setenv(SPOTIFY_CLIENT_SECRET = 'b742be8a81ba469794bd3146dac1d080')

access_token <- get_spotify_access_token()
```

## Gets the artists where the Spotify Id is missing
```{r}
missing_ids <- upcoming_shows1 %>%
  filter(is.na(Spotify))
```

```{r}
# Creates an empty dataframe to store the results
results_df <- data.frame(Name = character(0), Spotify = character(0))

# Iterates through each row in missing_ids
for (i in 1:nrow(missing_ids)) {
  # Get the value from the current row in missing_ids
  length <- missing_ids$Name[i]
  
  # Runs the Spotify search for the current value
  a <- spotifyr::search_spotify(
    q = length,
    type = 'artist',
    market = 'US'
  )
    # Checks if the search results are empty
  if (nrow(a) == 0) {
    # If there are no results, skip to the next iteration
    next
  }
  
  # Filters the results to include only the matching artist with followers
  filtered_results <- a %>% 
    filter(name == length & followers.total > 0) %>%
    select(name, popularity, followers.total, id, external_urls.spotify)
  
  # Find the maximum popularity within each group of the same name
  max_followers <- filtered_results %>%
    group_by(name) %>%
    slice_max(order_by = followers.total) %>%
    ungroup()
  
  # Append the results to the results dataframe
  results_df <- rbind(results_df, max_followers)
}

```

### Joins the artists with missing ids to the upcoming_shows1 df
```{r}
final_df <- upcoming_shows1 %>%
  left_join(results_df, by = c("Name" = "name")) %>%
  mutate(Spotify = coalesce(id, Spotify)) %>%
  select(1:4) %>%
  na.omit()
```

## Creates dataframe of top 5 tracks
```{r}
   
# Initialize an empty data frame to store the top tracks
top_tracks_df <- data.frame(
  artist_name = character(),
  artist_id = character(),
  duration_ms = integer(),
  id = character(),
  name = character(),
  popularity = integer(),
  stringsAsFactors = FALSE
)

# Iterates through each artist's Spotify ID
for (spotify_id in final_df$Spotify) {
  if (!is.na(spotify_id)) {
    # Gets the top tracks for the current artist
    artist_info <- spotifyr::get_artist(spotify_id)
    top_tracks <- spotifyr::get_artist_top_tracks(spotify_id)
    
    # Checks if top_tracks is empty
  if (length(top_tracks) == 0) {
      top_tracks <- data.frame(
        artist_name = artist_info$name,
        artist_id = spotify_id,
        duration_ms = NA,
        id = NA,
        name = NA,
        popularity = NA,
        stringsAsFactors = FALSE
      )
    } else {
      top_tracks <- top_tracks %>%
        mutate(artist_name = artist_info$name) %>%
        mutate(artist_id = spotify_id) %>%
        select(artist_name, artist_id, duration_ms, id, name, popularity) %>%
        top_n(5)
    }
    
    # Adds the top tracks to the data frame
    top_tracks_df <- bind_rows(top_tracks_df, top_tracks)
  }
}

# Resets row names (optional)
# rownames(top_tracks_df) <- NULL

# top_tracks_df

```

```{r}
app_df <- right_join(final_df, top_tracks_df, by = c("Spotify" = "artist_id")) %>%
  select(venue,
         show_date,
         Name,
         Spotify,
         name,
         id
  ) %>%
  mutate(track_uri = paste('spotify:track:',id,sep =""))

colnames(app_df) <- c('venue','show_date', 'artist', 'artist_id','song', 'song_id','track_uri')

write.csv(app_df, "C:/Users/mikek/Desktop/R Code/Spotify_Jambase/Spotify_JamBase/PlaylistCreator/app_df.csv")
```

```{r}
write.csv(upcoming_shows1, "C:/Users/mikek/Desktop/R Code/Spotify_Jambase/Spotify_JamBase/PlaylistCreator/upcoming_shows1.csv")
write.csv(top_tracks_df, "C:/Users/mikek/Desktop/R Code/Spotify_Jambase/Spotify_JamBase/PlaylistCreator/top_tracks_df.csv")
write.csv(results_df, "C:/Users/mikek/Desktop/R Code/Spotify_Jambase/Spotify_JamBase/PlaylistCreator/results_df.csv")
write.csv(final_df, "C:/Users/mikek/Desktop/R Code/Spotify_Jambase/Spotify_JamBase/PlaylistCreator/final_df.csv")
results_df
```

