---
title: "Jambase API"
author: "Mike Kaminski"
date: "2023-09-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r}
library(httr)
library(lubridate)
library(dplyr)
# url for the events page
url <- "https://www.jambase.com/jb-api/v1/events"

# date to get the next few months
future_date <- Sys.Date() %m+% months(3)

# gets the number of shows for the future date
countString <- list(apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
                    geoCityId ="jambase:4230765",
                    eventDateTo = future_date) # this is the Chicago geoCityId

countResponse <- VERB("GET",
                      url,
                      query = countString,
                      content_type("application/octet-stream"),
                      accept("application/json"))

countContent <- content(countResponse,"parsed")

numShows <- countContent$pagination$totalItems

# numPages <- countContent$pagination$totalPages

# queryString <- list(apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
#                     geoCityId ="jambase:4230765",
#                     perPage = 100,
#                     eventDateTo = future_date)
# 
# response <- VERB("GET", url, query = queryString, content_type("application/octet-stream"), accept("application/json"))
# all <- content(response, "parsed")
```

# Gets all the upcoming shows.
```{r}
# create an empty list to store the results
all_results <- list()

# Define  common parameters
common_params <- list(
  apikey = "e9bc7d9d-0946-43ec-a95e-b8f19cbbb6b1",
  geoCityId = "jambase:4230765",
  perPage = 100,
  eventDateTo = future_date,
  expandExternalIdentifiers = "true"
)

# Specify the number of pages to fetch
num_pages <- ceiling(numShows/100)

# Loop through each page
for (page in 1:num_pages) {
  # Create a copy of the common parameters and set the 'page' parameter
  query_params <- c(common_params, page = page)
  
  # Send the HTTP request
  response <- VERB("GET", url, query = query_params, content_type("application/octet-stream"), accept("application/json"))
  
  # Parse and store the response in the list
  all_results[[page]] <- content(response, "parsed")
}


all_results[[1]]$events[[1]]$performer[[1]]$`x-externalIdentifiers`[[5]]$identifier[[1]]

str(all_results[[1]]$events[[1]]$performer[[1]])
```

# Gets all the venues
If there's more than 1 performer at the event, then the venue is repeated.
```{r}
# Original Code
# venues <- lapply(all_results, function(x) {
#   lapply(x$events, function(event) {
#     event$location$name
#   })
# })

venues <-
  lapply(all_results, function(x) {
    lapply(x$events, function(event) {
      if (length(event$performer) > 1) {
        names <- rep(event$location$name, length(event$performer))
      } else if (length(event$performer) == 1) {
        names <- event$location$name
      } else {
        names <- NA  # or any other value you want to use for missing names
      }
      names
    })
  })

venues_col <- unlist(venues) %>% as.data.frame()
colnames(venues_col) <- "venue"
```

# Gets the date of the show
If there's more than 1 performer at the event, then the date is repeated.
```{r}
# Original Code
# shows <- lapply(all_results, function(x) {
#   lapply(x$events, function(event) {
#     event$startDate
#   })
# })

shows <-
  lapply(all_results, function(x) {
    lapply(x$events, function(event) {
      if (length(event$performer) > 1) {
        names <- rep(event$startDate, length(event$performer))
      } else if (length(event$performer) == 1) {
        names <- event$startDate
      } else {
        names <- NA  # or any other value you want to use for missing names
      }
      names
    })
  })

shows_col <- unlist(shows) %>% as.data.frame()
colnames(shows_col) <- "show_date"
```


# old code to get artist name
```{r}
# artists <-
#   value <- lapply(all_results, function(x) {
#   lapply(x$events, function(event) {
#     if (length(event$performer) > 1) {
#       names <- lapply(event$performer, function(performer) performer$name)
#     } else if (length(event$performer) == 1) {
#       names <- event$performer[[1]]$name
#     }
#     names
#   })
# })
# 
# artists_col <- unlist(artists) %>% as.data.frame()
# colnames(artists_col) <- "artists"
#   
```

# gets the performance date for each band
```{r}
perf_date <-
  venues <- lapply(all_results, function(x) {
  lapply(x$events, function(event) {
    if (length(event$performer) > 1) {
      names <- lapply(event$performer, function(performer) performer$`x-performanceDate`)
    } else if (length(event$performer) == 1) {
      names <- event$performer[[1]]$`x-performanceDate`
    }
    names
  })
})

perf_col <- unlist(perf_date) %>% as.data.frame()
colnames(perf_col) <- "perfdate"
```

# New code to get artist name as well as spotify_id
```{r}
# Initialize an empty list to store performer names and Spotify identifiers
performer_data <- list()

# Iterate through each result in all_results
for (result in all_results) {
  # Iterate through each event in the result
  for (event in result$events) {
    # Check if the event has performers
    if (length(event$performer) > 0) {
      # Iterate through each performer in the event
      for (performer in event$performer) {
        # Check if performer has external identifiers
        if (!is.null(performer$`x-externalIdentifiers`)) {
          # Find the entry with source "spotify"
          spotify_entry <- lapply(performer$`x-externalIdentifiers`, function(entry) {
            if (entry$source == "spotify") {
              return(entry$identifier[[1]])
            }
          })
          # Remove NULL values (entries other than "spotify")
          spotify_entry <- Filter(function(x) !is.null(x), spotify_entry)
          
          # Get the performer name
          performer_name <- performer$name
          
          # Create a list containing both performer name and Spotify identifiers
          performer_data_entry <- list(name = performer_name, spotify = spotify_entry)
          
          # Add the data for this performer to the list
          performer_data <- append(performer_data, list(performer_data_entry))
        }
      }
    }
  }
}

# performer_data[[1]]$name
# performer_data[[1]]$spotify
# str(performer_data[[1]])

performer_df <- data.frame(
  Name = sapply(performer_data, function(entry) entry$name),
  Spotify = sapply(performer_data, function(entry) {
    if (length(entry$spotify) > 0) {
      return(entry$spotify[[1]])
    } else {
      return(NA)
    }
  })
)

```


# Merges dataframes
```{r}
upcoming_shows <- cbind(venues_col,shows_col,performer_df) %>%
  mutate(show_date = as.Date(show_date,format = "%Y-%m-%d")) %>%
  filter(!grepl("Sofar",venue, ignore.case = TRUE)) %>%
  filter(!(venue %in% c("Douglas Park",
                     "Hyde Park Jazz",
                     "Fairmont Chicago Millennium Park",
                     "Epiphany Center for the Arts",
                     "On Tour Brewing")))

upcoming_shows %>% group_by(venue) %>% summarise(count = n()) %>% arrange(desc(count))
upcoming_shows %>% summarise(count = n()) %>% arrange(desc(count))
upcoming_shows %>% filter(venue %in% 'United Center')
```

# Removes duplicate Spotify Ids
```{r}
upcoming_shows1 <- upcoming_shows %>% distinct(Name, Spotify)
```


# END